---
title: "Homework 6"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(janitor)
library(modelr)
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

# Problem 2
```{r}
urlfile="https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
post_homicide = read_csv(url(urlfile))

set.seed(1)
post_homicide =
  post_homicide %>% 
  mutate(city_state = paste(city, state, sep=", ")) %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  filter(victim_race %in% c("Black", "White")) %>% 
  mutate(
    homicide_solved = as.numeric(disposition == "Closed by arrest"),
    victim_race = fct_relevel(victim_race, "White"),
    victim_age = as.numeric(victim_age),
    victim_sex = fct_relevel(victim_sex, "Female")
  ) %>% 
  select(city_state, homicide_solved, victim_age, victim_sex, victim_race)
```

### Odds Ratio and Confidence Interval for Baltimore, MD
```{r}
baltimore_reg =
  post_homicide %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(homicide_solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>%
  tidy() %>% 
  filter(term == "victim_sexMale") %>% 
  select(term, estimate, std.error) %>% 
  mutate(
    odds_ratio = exp(estimate),
    low_conf = exp(estimate - 1.96*std.error),
    upper_conf = exp(estimate + 1.96*std.error)) %>% 
  select(-estimate, -std.error)
 
baltimore_reg %>% 
  knitr::kable(digits = 3)
```
Homicides in which the victim is male are significantly less like to be resolved than those in which the victim is female. 

### Odds Ratio and Confidence Interval for All Cities
```{r}
cities_reg = 
  post_homicide %>%
  nest(data = -city_state) %>% 
  mutate(model = map(data, ~glm(homicide_solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
         results = map(model, broom::tidy)) %>% 
  select(-data, -model) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state, term, estimate, std.error) %>% 
  mutate(
    odds_ratio = exp(estimate),
    low_conf = exp(estimate - 1.96*std.error),
    upper_conf = exp(estimate + 1.96*std.error)) %>% 
  select(-estimate, -std.error)

cities_reg %>% 
  knitr::kable(digits = 3)
```

#### Plot
```{r}
cities_reg %>% 
  mutate(city_state = fct_reorder(city_state, odds_ratio)) %>% 
  ggplot(aes(x=city_state, y = odds_ratio)) +
  geom_point(stat = "identity", shape = 10) +
  geom_errorbar(aes(ymin = low_conf, ymax = upper_conf), width = 0.4) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 90)) +
  geom_hline(yintercept=1, color='black', linetype='dashed', alpha=.5)+
  labs(
    x = "City, State",
    y = "Odds Ratios"
    )
```
According to the plot, in most cities with significant odds ratios, homicides in which the victim is male are significantly less like to be resolved than those in which the victim is female.  The cities in which the homicides in which the victim is male are significantly more likely to be resolved have a very wide confidence interval and include the null value (OR = 1). Therefore, the victim's sex may not have a significant difference on whether or not the homicide will be resolved. 

# Problem 3
```{r}
child_bwt = read_csv("data/birthweight.csv")

child_bwt %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) 
```

The model I propose is a linear regression model with `bwt`, baby's birthweight (continuous, lbs), as the outcome and `wtgain`, mother's weight gain during pregnancy (continuous, lbs), as the main exposure. I hypothesize that a mother's weight at delivery as a positive association with baby's birthweight, meaning that a higher mother's weight at delivery is associated with a higher baby's birthweight. If the expecting mother gains a large amount of weight, there is a higher chance that the baby will be born weighing more than a baby born from a mother who does not gain much weight during her pregnancy. I hypothesize that `momage`, mother's age at delivery (continuous, years), `delwt`, mother's weight at delivery continuous, lbs), and `fincome`, family monthly income (continuous, in hundreds, rounded) affect the association between baby's birthweight and mother's weight gain during pregnancy.

## Linear Regression Model Assessing the Association Between `bwt` (baby's birthweight, lbs) and `wtgain` (mother's weight gain during pregnancy, lbs)
```{r}
child_bwt %>% 
  mutate(
    bwt = bwt*0.0022046226
  )

bwt_linear = lm(bwt ~ wtgain + momage + delwt + fincome, data = child_bwt)

resids_fitted <-
  child_bwt %>% 
  add_residuals(bwt_linear, var = "resids") %>% 
  add_predictions(bwt_linear, var = "fitted_values") %>% 
  ggplot(aes(x = fitted_values, y = resids))+
  geom_point() +
  geom_line(color = "blue") +
  labs(
    title = "Residuals Against Fitted Values Plot",
    x = "Fitted Values",
    y = "Residuals"
  )

resids_fitted
```

## Compare Linear Models
```{r}
bwt_linear2 = lm(bwt ~ blength + gaweeks, data = child_bwt)

child_bwt %>% 
  mutate(
    bhead = bhead* 0.3937007874,
    blength = blength* 0.3937007874,
  )

bwt_linear3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = child_bwt)
```

## `crossv_mc`
```{r}
compare_cv = 
  crossv_mc(child_bwt, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    bwt_linear = map(train, ~lm(bwt ~ wtgain + momage + delwt + fincome, data = .x)),
    bwt_linear2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    bwt_linear3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_linear1 = map2_dbl(bwt_linear, test, ~rmse(model = .x, data = .y)),
    rmse_linear2 = map2_dbl(bwt_linear2, test, ~rmse(model = .x, data = .y)),
    rmse_linear3 = map2_dbl(bwt_linear3, test, ~rmse(model = .x, data = .y)))

compare_cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```

